Extinction simulation on the metaweb

### 2022-07-25 random_network.Rmd
Make lm for random network

```{r}
sim_sp_dec_inc %>%
  filter(str_detect(metric, "_ff")) %>%
  mutate(
    metric = var_replacement()[metric],
    type = str_to_sentence(type)
    ) %>%
  ggplot(aes(x = nb_ext, y = value, color = type)) +
  geom_line() +
  geom_point(
    data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    )) +
  geom_smooth(data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    ), color = "black") +
  facet_wrap(~metric, scale = "free_y") +
  labs(y = "Network metric values", x = "Number of species removed",
    color = "Trophic level scenario") +
  theme(legend.position = "bottom")
p_ext_node
```

>>>>

```{r}
p_ext_sp <- sim_sp_dec_inc %>%
  filter(str_detect(metric, "_ff")) %>%
  mutate(
    metric = var_replacement()[metric],
    type = str_to_sentence(type)
    ) %>%
  ggplot(aes(x = nb_ext, y = value, color = type)) +
  geom_line() +
  geom_point(
    data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    )) +
  geom_smooth(data = rand_sp_met %>%
    filter(str_detect(metric, "_ff")) %>%
    mutate(
      metric = var_replacement()[metric],
      type = str_to_sentence(type)
    ), color = "black") +
  facet_wrap(~metric, scale = "free_y") +
  labs(y = "Network metric values", x = "Number of species removed",
    color = "Trophic level scenario") +
  theme(legend.position = "bottom")
p_ext_node
```

```{r}
model_res <- rand_sp_met %>%
  select(metric, value, nb_ext) %>%
  filter(str_detect(metric, "_ff")) %>%
  nest_by(metric) %>%
  mutate(
    mod = list(lm(value ~ nb_ext, data)),
    coefs = list(broom::tidy(mod))
  ) %>%
  unnest(coefs) %>%
  filter(term == "nb_ext")
```
